\url{https://tabs.ultimate-guitar.com/tab/phil-wickham/house-of-the-lord-chords-3641219} \par
\url{https://essentialworship.com/songs/phil-wickham/house-of-the-lord/} \par

\newcommand{\owelkh}[0]{
  ^{C} There’s joy in the house of the ^{Csus2}Lord. \\
  ^{C} There’s joy in the house of the ^{Csus2}Lord ^{Gsus} ^{Fadd9}today. ^{F2} \\
  And we won’t be ^{Fadd9}quiet, we shout out ^{G}Your ^{C}praise. \\
  ^{C} There’s joy in the house of the ^{Csus2}Lord. \\
  ^{C} Our God is surely ^{Csus2}in ^{Gsus} this ^{Fadd9}place. ^{F2} \\
  And we won’t be ^{Fadd9}quiet, we shout out ^{G}Your ^{C}praise.
}

\newcommand{\qhaudn}[0]{
  We were the ^{C}beggars, now we're ^*{Csus4}royal- ^{C}ty. \\
  We were the ^{C}prisoners, now we're ^{Csus4}running ^{C}free. \\
  We are for^{Am7}given, accepted, re^{Faad9}deemed by His ^{C}grace. \\
  Let the ^{G}house of the ^{Fadd9}Lord sing ^{C}praise.
}

\begin{verse}[label-format={Verse 1}]
  We ^{C}worship the God who was. \\
  We ^{C}worship the God who is. \\
  We ^{C}worship the God who ^*{Am7}ever- ^{Gsus}more will ^{Fadd9}be.
\end{verse}

\begin{prechorus}
  He ^{C}opened the prison doors. \\
  He ^{C}parted the raging sea. \\
  My ^{C}God, He ^{Am7}holds the ^*{Gsus}victo- ^{Fadd9}ry.
\end{prechorus}

\begin{chorus}
  \owelkh \\
  \owelkh
\end{chorus}

\begin{verse}[label-format={Verse 2}]
  We ^{C}sing to the God who heals. \\
  We ^{C}sing to the God who saves. \\
  We ^{C}sing to the God who ^{Am7}always ^{G}makes a ^{Fadd9}way.
\end{verse}

\begin{prechorus}
  'Cause He ^{C}hung upon that Cross. \\
  Then He ^{Dm7}rose up from that grave. \\
  My ^{Am7}God’s still ^{G}rolling stones a^{Fadd9}way.
\end{prechorus}

\begin{chorus}
  \owelkh
\end{chorus}

\begin{bridge}
  \qhaudn
\end{bridge}

\begin{bridge}[label-format={All}]
  'Cause We were \qhaudn
\end{bridge}

\begin{chorus}
  \owelkh \\
  \owelkh
\end{chorus}

\begin{verse}[label-format={????}]
  ^{C} \quad ^{Csus2} \quad ^{C} \quad ^{Csus2} \quad ^{|} \quad ^{Fadd9} \quad ^{Csus2/F} \quad ^{Fadd9} \quad ^{G} \\
  ^{C} \quad ^{Csus2} \quad ^{C} \quad ^{Csus2} \quad ^{|} \quad ^{Fadd9} \quad ^{Csus2/F} \quad ^{Fadd9} \quad ^{G} \\
  ^{C2} \quad ^{Gsus} \\
  \\
  ^{Csus2} \quad ^{C} We shout out ^{Csus2}Your ^{Fadd9}praise \quad ^{Csus2/F} \quad ^{Fadd9} \quad ^{G} \\
  ^{C} \quad ^{Gsus} \quad ^{F} \quad ^{Gsus} \\
  \\
  ^{C} \quad ^{Csus2} \quad ^{C} We shout out ^{Csus2}Your ^{Fadd9}praise. \\
  ^{Csus2/F} There is joy in this ^{Fadd9}house. There is ^{Csus2/F}joy in this house ^{C}today. ^{Csus2} \quad ^{C} \\
  We shout out ^{Csus2}Your ^{Fadd9}praise. ^{Csus2/F}  ^{Fadd9} We shout out ^{Csus4}Your ^{C} praise.
\end{verse}
